\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cEAirship{}}

You are \cEAirship{} (\cEAirship{\They}/\cEAirship{\Them}). You are a fire pixie from the Court of Elements, and it is your pleasure and delight to be helping your two absolute best friends \cMAirship{} and \cFTitan{} accomplish things that are going to change Neverland as pixie-kind knows it. A lot of people think of destruction and anger when they think of fire. You think of candles in windows, warm soup, and summer bonfires. Connection.

\cMAirship{} and you are working on a new way to enable connection. A new type of transportation that the two of you call an ``Airship.'’ You wanted to call it a “Fireship” since it is fire magic that makes it float, but \cMAirship{} said that since it travels through the air, that it was a more appropriate name. Anyway, the thing is that Pixies are small. Quite small. Especially compared to… well… everything. Which means that it takes a lot of work to move things. Does anyone care how long it takes to carry enough dewdrops to last two years? You can only fit like 6 or 8 in a wheelbarrow at a time! But if pixies had something that floated - not something held up by dozens of pixies beating their wings as hard as they could - but something that floated all by itself, why you could move all kinds of things with ease!

That's the vision. It's been a long, hard slough to get this close to making it a reality. You've worked and sweated and struggled over problems that seemed impossible to solve. You've had to… ah… bend a few rules along the way. You “borrowed” a little more pixie dust than you're technically allotted (4 units to be exact), and even a few units of Season components (5 units to be exact). But you're an Element pixie. You know that the court makes spare Season components. \cMAirship{} says it's the same for the Magic and Maker Pixies. They always keep extra pixie dust on hand. So no harm, no foul right? 

Except for the final piece: the two of you have tried everything you could think of to get around it, but the truth is that for long flights (more than about 20 minutes), or heavy loads (more than about 2000 dewdrops), you either need so many fire pixies to heat the air inside the balloon-like canopy that you might as well carry the stuff yourself, or you need something that will distribute the heat evenly and consistently. And this is where \textbf{iron} comes in. You tried with rocks, you tried with glass, you even tried with copper. But there is no getting around the fact that iron has weird interactions with pixie magic that you hope will allow a single fire pixie to lift and maneuver an entire airship full of supplies, maybe with the help of an air pixie or a fast flyer from the Court of Structure to help with steering.

The only place to get iron is the mortal world. You plan to try to sneak through the open portal and snag some tonight. Or you could end up on the away team, but ugh, having to wait two whole years before you can see if your plan works? No way; that'd take too long! And why sneak? Well you don't think that the Structure Pixies will \textbf{let} you bring iron into Neverland, at least not until you prove how cool your concept is (and that it works; which it doesn't without the iron.)

While passing the time waiting for the portal to open, you went to a tea mixer a few months ago, and met \cFTitan{}. The two of you instantly hit it off and became close friends. \cFTitan{\They} dream\cFTitan{\plural} almost as big as you do. \cFTitan{} confided to you that \cFTitan{\they} want to raise the Titans that were left as mere candle flickers of their former blazing glory after they saved Neverland. You think that it's a very noble thing to do to revive them, and you're happy to support \cFTitan{} in the process. Although sometimes you do worry that they might not be so happy to come back to a world where pixies are using Iron to make transportation of supplies easier when the Titans gave up their existence to prevent iron from destroying Neverland\ldots


\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Make the airship work by acquiring and installing a piece of iron. Then present the idea to the Court of Structure and win their approval to build more.
	\item Support \cFTitan{} in reviving the Titans.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cMAirship{}} Your best friend of decades, with whom you have been working on designs for an``airship'’ that will revolutionize pixie work by drastically increasing efficiency.
	\contact{\cFTitan{}} Your recently met new best friend. The two of you are thick as thieves, and you are happy to help \cFTitan{\them} with \cFTitan{\their} plans to revive the Titans, as long as the titans wont be mad at you for working with Iron.
\end{contacts}

\end{document}
