\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cEHead{}}

You are \cEHead{} (\cEHead{\They}/\cEHead{\Them}), an Air Pixie, and the leader of the Court of Elements. Tonight was supposed to be nice and easy. A little welcome home celebration for the previous Away Team, a little send off soiree for the next Away Team, a little celebration for your tremendously hard working court members who have once again accomplished something that by all rights is a miracle.

But instead, you have a crisis on your hands. As you did your final inventory of the units of seasons being brought in and prepared to be transferred through the portal (when it opens), you found something was off. Not just off, missing! 20 whole units were missing (enough for an entire season)! Every go around, your Court assembles 170 units of Seasons (20 per season, plus 10 extras split as evenly as possible between). There's never been a need for the extras, which is why over the millenia, this extra has been winnowed down to so little. - Unfortunately the season units only keep for about two years, and they take a very long time to make, especially to your exacting standards. But now, tonight, not only are your extras missing, but you are somehow SHORT 10 units. That's 20 units missing. 20 units \textbf{stolen}. You keep the account books yourself. Your Structure Pixie Contact reviews the books every month. There's no chance that you just “miscounted” or something. (OOC Note: this is an NPC; they do not appear in this larp.)

How are you supposed to make 10 more seasons units in just a couple of hours?!? You need all of the raw materials, and possibly pixie dust (see greensheet) to make them, and they'll be terribly rushed and sloppy. But somehow you'll need to help your court do it, all while managing the shit you expect to rain down from the Structure Pixies, especially \cSHead{}, whom you just told about the problem \textit{(OOC Note: you literally just told \cSHead{\them}, \cSHead{\they} \cSHead{\have}n't had a chance to respond to your news before game start).}

All of this has quite honestly pushed from your mind what should have been the primary focus of the night: \cELove{}, your sweetheart, is returning from the Away Team tonight! The two of you parted just after a fight, but those happen to every couple. You don't even remember what the fight was about. Ah, but absence makes the heart grow fonder. You were looking forward to asking  \cELove{} to move in with you, except that now it has to wait, because the fate of all of Neverland rests on your shoulders.

And of course, there must be a new Away Team to manage the distribution of the seasons.  You don't know who to send. \cETitan{} and \cFTitan{} are the most exhausting pixies you've ever had the misfortune to deal with, except of course for \cEAirship{} and \cMAirship{}. You know what, you can't decide which pair is worse. Regardless, you are certain that neither pair should be sent together. So depending on who the other Courts choose to send, you could send one of them, or you could send \cESweet{}, but \cESweet{\theyare} so very sweet, and kind, and gentle. You worry that the harsh realities of the Mortal World would change \cESweet{\them} for the worse. It's one of the many beauties of Neverland: purity and innocence are not weakness here, naivete isn't an insult, optimism isn't a flaw. You don't want to be responsible for putting \cESweet{} in a situation that destroys \cESweet{\their} ability to see the good in the world.


\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Find out what happened to the missing Seasons units and make \textbf{sure} it never happens again.
	\item Find a way to hastily build replacement units.
	\item Reunite with \cELove{} and propose that the two of you move in together.
	\item Help \cSHead{} decide on an away team. You aren't sure who among the Element Pixies you should send.
\end{itemz}

\begin{itemz}[Notes]
	\item The Court of Elements always makes 10 extra units of season components, just in case. But the extras haven't been needed in centuries. Each season component is good for about 2 years before it loses it's potency.
\end{itemz}

\begin{contacts}
	\contact{\cELove{}} Your sweetheart, who has been on the Away Team these past two years. You are very much looking forward to the reunion. Surely the fight has blown over in two whole years.
	\contact{\cSHead{}} The leader of all of Pixie Hollow, who is probably about to blame you and your court for something that is most definitely \textbf{not} your fault.
	\contact{\cEAirship{}} The most frustrating, troublemaking pixie you've ever had the misfortune to deal with, aside from maybe \cETitan{}.
	\contact{\cETitan{}} The most frustrating, troublemaking pixie you've ever had the misfortune to deal with, aside from maybe \cEAirship{}.
	\contact{\cESweet{}} A pixie almost too sweet and innocent even for Neverland. Would not do well on the Away team.
\end{contacts}

\end{document}
