\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cELove{}}

You are \cELove{} (\cELove{\They}/\cELove{\Them}), and a Water Pixie of the Court of Elements. You are returning from the Away Team, having left two years ago, in the midst of a massive argument with \cEHead{}, your romantic partner. You aren’t done with that argument and honestly wouldn’t mind if \cEHead{} sent \cEHead{\them}self on the next away mission.

You and \cEHead{} had been romantically close for a number of years, but eventually, little things started to get to you. Most particularly, \cEHead{\their} perfectionism. Being in the same court, you saw every day how particular \cEHead{} is about how the season components need to be built just so, and organized \cEHead{\their} way, and on \cEHead{\their} schedule. You are a water pixie; not to be stereotypical, but you really much prefer going with the flow. You really don’t care if every aspen leaf is exactly the same shade of yellow. You fondly remember a time from before \cEHead{} was the leader of the court, when \cEHead{\they} \cEHead{\were} far more spontaneous, and far less exacting.

So the two of you were fighting. Arguing over something or other; probably how the very last snowflake you made didn’t have perfectly 60 degree angles or whatever. Who cares? The details are too small for most humans to see, and they don’t have the patience to stop and examine an individual snowflake anyway. Someone else had been assigned to the away team from the Court of Elements (OOC Note: that pixie is not in this game), but they were reluctant to go, so you shouted something mean and marched through the portal yourself.

After two years of reflection, you are still mad. You still don’t think that nitpicking and micromanaging is a sustainable way to run a court. And you miss your friend - who \cEHead{} was before all of the responsibility. You were planning to give \cEHead{} a piece of your mind the moment the portal opened, until what happened a week ago.

Despite the strict prohibition on exploring the mortal world that \cSPM{} had instituted, you woke up one morning to find \cFLost{} and \cMChange{} gone. You waited all day at headquarters, watching \cSPM{} pacing anxiously. In the fading light of dusk, you saw a distress signal. Such a signal was only to be used in the most dire of circumstances, as it might be noticed by the denizens of the mortal world. 

You and \cSPM{} hastened to the source - a garden shed. \cFLost{} was pinned beneath a cascade of rusty old nuts, bolts, nails and screws that had fallen from a spilled container from a higher shelf. \cFLost{\Their} light was dim and flickering. You’d never seen a pixie so weak or so hurt. \cMChange{} was crying hysterically, while trying to pull the bits and bobs off of \cFLost{}. Every time \cMChange{} touched one of the metal bits, it burnt \cMChange{\their} skin again. Clearly \cMChange{\they} had been trying for hours to free \cFLost{}, to no avail, before \cMChange{\they} finally thought to call for help.

You looked to \cSPM{}, and saw them frozen in shock. Spreadsheets and time tables weren’t going to fix this - weren’t going to save a Pixie from cold iron. You made a face and got to work. Why must you always be the only practical one? You pulled \cMChange{} away, wrapped \cMChange{\their} blistered hands in leaves and soothing, cooling mud, and fetched sticks to build little levers that were safe to touch. You directed the other two Pixies to help you get \cFLost{} free. At least the three of you were able to hold \cFLost{\them} as \cFLost{\their} light went out.

The tragedy has been mind-numbing. What are you going to tell everyone when you get back? How do you even start such a heavy conversation with your remaining teammates? So you haven’t. And \cSPM{} hasn’t either. And \cMChange{} glazes over with horror every time anything comes close to reminding \cMChange{\them} of what happened. But you’ve got to say something. That portal opens in 15 minutes. \textit{(OOC Note: this is partially a contrivance to allow PCs to play out this interaction and establish character dynamics.)}


\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Figure out what to tell everyone about what happened to \cFLost{}. Support \cSPM{} and especially \cMChange{} as best you can.
	\item Have a long conversation with \cEHead{} about how \cEHead{\they} run\cEHead{\plural} the Court of Elements. You aren’t opposed to making up, but you are opposed to sweeping the problems you see under the rug.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cEHead{}} Your (former?) romantic partner, and the head of the Court of Elements. You parted two years ago in the midst of a fight about \cEHead{\their} controlling nature.
	\contact{\cSPM{}} The Pixie in charge of the Away Team. You do \textbf{not} envy \cSPM{\their} position right now, as \cSPM{\they} \cSPM{\are} expected to provide a full report to everyone upon the return of the away team.
	\contact{\cMChange{}} The pixie who found \cFLost{} in trouble. \cMChange{\They} \cMChange{\have} been deeply affected, and while you want to help, you’re not really sure how to do that.
\end{contacts}

\end{document}
