\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cESweet{}}

You are \cESweet{} (\cESweet{\They}/\cESweet{\Them}). You are a light pixie with a soft heart and a sunny disposition. Your favorite seasons components to build are rainbows and dappled light through summer leaves. Light is a core component of many of the most precious, liminal moments of the seasons.

You see how hard all of your friends work, especially in the Court of Elements, all year round, for two years, and then you just send it through a portal and it’s gone. You start all over again. It’s kind of… gloomy. Like a cloudy day with no sun. There’s no break, there’s no real celebration, and there’s no chance to see the results of your hard work unfolding.

That’s not fair. It’s not fair to you, and it’s not fair to anyone else. So you’re going to fix it! You’ve found three like-minded friends who are going to help you make this a reality: \cSLibrarian{}, \cFHeart{}, and \cMIron{}. Together you have a secret plan to prevent the portal from closing so everyone can watch the seasons spread through the mortal world. \cMIron{} has squirreled away quite a stockpile of pixie dust to power the ritual that the librarian/archivist designed. The ritual happens in 2 parts. The four of you must complete most of it here, and then exactly 1 of you must be part of the away team to perform the final step on the mortal side of the barrier. Then the portal will be blown back open, never again to close. You would very much like to be the one on the mortal side, in case the plan doesn’t work.

Other than that\ldots You’re not really sure what to do tonight. You had this idea that you were going to try to liven up the event and have an actual party, but your smile faded, and your heart sank as you looked around the room. \cFButterfly{} looks upset. So does \cMHead{}. \cSHead{} and \cEHead{} have their heads close together, whispering, and they both look worried. Whatever is going on is not good. So you guess it’s time to roll up your sleeves and bring a little light of hope.

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Work with \cSLibrarian{}, \cFHeart{} and \cMIron{} to permanently open the portal to the mortal world.
	\begin{itemize}
		\item Perform the Neverland side of the ritual before the Away Team is sent off.
		\item Get exactly one of you (preferably you personally) on the Away Team, to complete the last step (in the last 15 minute of game).
		\item If the plan to permanently open the portal fails, you at least can go see it for yourself.
	\end{itemize}
	\item Try to cheer everyone up. \textit{(OOC Note: You can play this as oblivious, or as emotionally savvy, as you like.)}
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cSLibrarian{}} One of your co-conspirators, who designed the ritual you will be executing on tonight.
	\contact{\cFHeart{}} A fellow conspirator in trying to keep the portal from closing. \cFHeart{\They} worr\cFHeart{\pluralY} about the animals and plants of the mortal world without Flora and Fauna pixies to look after them.
	\contact{\cMIron{}} A fellow conspirator in trying to keep the portal from closing. Very practical. Sometimes a little boring because of it. Still a good friend.
\end{contacts}

\end{document}
