\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cETitan{}}

You are \cETitan{} (\cETitan{\They}/\cETitan{\Them}). You are an adventurous earth Pixie in cahoots with \cFTitan{} to change Neverland by reviving the Titans. You’ve always been fascinated by the story of the Titans, and the more you dug into the history, the more intrigued you became. 

You find it particularly fascinating that all four left behind stone remnants. The deeper you dug, the more you found, until one day you ran into (literally) \cFTitan{}, who had discovered the location of those remnants. The two of you joined forces, and have been planning ever since. Obviously the preparations haven’t been easy. This is no simple task, and you’ve been researching, planning, and preparing for years. On multiple occasions you have wanted to give up; the task seemed impossible. But every time, you’ve found your way through. A recent addition to your team, \cEAirship{}, has been an invaluable cheerleader for the two of you.

For the final preparation step, you and \cETitan{} had to borrow some of the spare pixie dust that the Magic pixies keep on hand (4 units), and some of the extra seasons components that the Element pixies make as buffer (5 units) - you would never have taken these without permission, except that no one believes reviving the Titans is even possible. And the resources you took are definitely extras. You triple checked. You have already spent these (pre-game) on preparations, so only the very last step remains. A ritual for four Pixies that must be completed once in Neverland, and once in the Mortal World (see greensheet for more information). You’ll have to recruit one more pixie to your cause to make the four you need.

You kind of hope that your “one more” can be \cMAirship{}. \cMAirship{\Theyare} a super cute pixie from Makers and Magic. Prior to \cEAirship{} joining this project, you’d never had much contact with the Court of Makers and Magic, so you’d never met \cMAirship{}. But now that the two of you have crossed paths a few times, you’d really like to get to know them better, and you’re pretty sure \cMAirship{\they} feel\cMAirship{\plural} the same way. Hopefully \cMAirship{} doesn’t get quite as tongue-tied around you, otherwise there might not be much conversation. Maybe you can get \cEAirship{} to introduce you? \cEAirship{} and \cMAirship{} seem to be pretty good friends already.
 

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Revive the Titans with the help of \cFTitan{} and \cEAirship{}.
	\item Get to know \cMAirship{} and see if \cMAirship{\theyare} interested in maybe starting a romantic relationship.
\end{itemz}

\begin{itemz}[Notes]
	\item The Court of Elements always makes 10 extra units of season components, just in case. But the extras haven't been needed in centuries. Each season component is good for about 2 years before it loses it's potency.
\end{itemz}

\begin{contacts}
	\contact{\cFTitan{}} A fellow pixie who shares your belief that not only is it possible to revive the Titans, but that you are morally obligated to do so.
	\contact{\cEAirship{}} A late addition to your quest to revive the titans; \cEAirship{} has been an invaluable cheerleader when the project has felt impossible.
	\contact{\cMAirship{}} Your crush. You haven’t spoken much yet.
\end{contacts}

\end{document}
