\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cFButterfly{}}

You are \cFButterfly{} (\cFButterfly{\They}/\cFButterfly{\Them}). Your specialty is with Lepidoptera (butterflies and moths). They don’t mind that you are shy and nervous and socially anxious. They don’t make loud noises, or sudden movements, or chase you, or demand you do public speaking. (OOC Note: it is up to you as a player how much you want to respectfully lean into the social anxiety - no caricatures please. Be aware that several other characters in game know that this character has something akin to social anxiety, so you will not be without support should you choose to explore this).

While normally you respect \cFHead{} (one of the highest ranking Flora and Fauna pixies, and head of the delegation tonight) right now you are rather mortified by \cFHead{\them}. \cFHead{} decided that you should be in charge (\textbf{in charge!}) of the lunar moth / solar butterfly migration that happens while the portal is open tonight. That means you’re gonna have to talk to people! And organize them! And stuff! (Maybe you could find a Structure Pixie to hide behind? \textbf{They} could do the talking.)

You hope everything will be easier once \cFLost{} comes back from the Away Team. With your nesting partner gone, you’ve felt extra out of sorts these past two years. \cFLost{} has the patience of a tortoise, always took your anxiety seriously, and helped support you through everything. In the meantime, your metamour, \cMHead{} has tried to support you. The two of you have never been particularly close, and \cMHead{} is busy with the many demands on \cMHead{\their} time as head of the Court of Magic and Makers. But it’s very sweet that \cMHead{\they} \cMHead{\have} tried; and really, \cMHead{\they} \cMHead{\have} been getting better at it.

So now, you and \cMHead{} are clustered close to the place where the portal will open. For about 20 minutes before the portal actually opens, the air in that space becomes increasingly translucent, and allows pixies to see the shadows of the away team on the other side of the portal before it opens. One, two, three\ldots three? Why do you only see three shadows on the other side of the portal?  You turn toward \cMHead{} who is standing beside you. The look in \cMHead{\their} eyes tells you \cMHead{\they} \cMHead{\are} having the same terrible, impossible thought as you. \textit{(OOC: the two of you will start in front of where the portal will open. You haven’t yet had a chance to voice anything to \cFButterfly{}, as you were waiting to see if something would change and a fourth shadow would appear. It will still be 15 minutes in game before the portal actually opens and you can see for sure what is happening.)}

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Find out what happened to the away team. Something is clearly not right.
	\item Conduct the Solar Butterfly / Lunar Moth migration (see greensheet). If possible, recruit a Structure pixie to do most of the talking and pixie wrangling for you.
	\item Practice self care and take breaks as you need to manage your social anxiety.
\end{itemz}

\begin{itemz}[Notes]
	\item Flora and Fauna pixies tend to understand ``goodbye'' better than most other pixies, since animals and plants don’t live forever the way pixies do. They still aren't very good at it.
\end{itemz}

\begin{contacts}
	\contact{\cFLost{}} Your nesting partner, best friend, and biggest helper in managing your social anxiety. You have been looking forward to having them back tonight, but now there is a growing pit of anxiety in your stomach.
	\contact{\cFHead{}} Your mentor, who put you in charge of the migration tonight.
	\contact{\cMHead{}} Your metamour. Both of you have been dating \cFLost{} for many years. The two of you have always been friendly, but have grown closer these past two years.
\end{contacts}

\end{document}
