\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cFHeart{}}

You are \cFHeart{} (\cFHeart{\They}/\cFHeart{\Them}). You are a sweet and kind Flora and Fauna pixie, with expertise in Roses and their ilk. Like roses, you can be beautiful to look at, and even beautiful to work with, but handled wrong, you too have thorns. And you are not afraid to let anyone who questions your vision have a taste. (OOC Note: You may interpret this as a flavor of vanity, or pride, or something else, or not play with it at all if you don’t feel like it.)

You see just how important having the help of Flora and Fauna pixies are to Neverland. Things flourish here in a way that is simply not possible in the human world (or so you’ve been told; you’ve never seen it). While the sun is up, you love helping plants grow and bloom and reach their full potential. But when the sun sets, and you are curled up in your cozy armchair with a mug of chamomile tea, you worry about all the living things in the human world that don’t have someone to take care of them. How scared must the baby mice be? How hard must the blackberries struggle to grow?

You understand that extended contact between Neverland and the Human World was dangerous in the past. Cold Iron is no joke. But we know better now. We know how to recognize it. So we know how to avoid it. And animals and plants aren’t made of iron. There’s no reason to prevent the Flora and Fauna pixies from helping living things in both realms. Luckily, you’ve found some like-minded pixies, and together you have a \textbf{secret} plan to do something about this. \cSLibrarian{}, \cESweet{}, and \cMIron{} all have their reasons to want the portal to stay open. 

Naturally you have to wait for the portal to open before you can prevent it from closing, so the four of you have been preparing for tonight for some time. \cMIron{} has squirreled away quite a stockpile of pixie dust to power the ritual that the librarian/archivist designed. The ritual happens in two parts. The four of you must complete most of it here, and then \textbf{exactly one} of you must be part of the away team to perform the final step on the mortal side of the barrier. Then the portal will be blown back open, never again to close. You would very much like to be the one on the mortal side, in case the plan doesn’t work.

It will be a lot of work taking care of everything in the Mortal World too, but you know that all of those living things deserve the same care and support as the ones in Neverland get. You hope that the other Flora and Fauna pixies are as excited as you by the opportunity you are about to create. You are especially worried about \cFWanabe{}. \cFWanabe{\They} \cFWanabe{\are} among the youngest Flora and Fauna pixies, and \cFWanabe{\they} always seem\cFWanabe{\plural} so unhappy to you. You can’t imagine why, but maybe you should find out? Maybe sharing your little surprise with \cFWanabe{\them} could cheer \cFWanabe{\them} up? Or maybe you shouldn’t tell \cFWanabe{\them}, would \cFWanabe{\they} try to stop you?

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item 
	\begin{itemize}
		\item Perform the Neverland side of the ritual before the Away Team is sent off.
		\item Get exactly one of you (preferably you personally) on the Away Team, to complete the last step (in the last 15 minutes of game).
		\item If the plan to permanently open the portal fails, you at least can go see it for yourself.
	\end{itemize}
	\item Get to know \cFWanabe{} and see if you can cheer them up somehow.
\end{itemz}

\begin{itemz}[Notes]
	\item Flora and Fauna pixies tend to understand ``goodbye'' better than most other pixies, since animals and plants don’t live forever the way pixies do. They still aren't very good at it.
\end{itemz}

\begin{contacts}
	\contact{\cSLibrarian{}} One of your co-conspirators, who designed the ritual you will be executing on tonight.
	\contact{\cESweet{}} One of your co-conspirators; a Pixie who could give you a run for your money as the sweetest Pixie in Pixie Hollow.
	\contact{\cMIron{}} One of your co-conspirators, who has been squirreling away the massive amounts of pixie dust that this ritual will require.
	\contact{\cFWanabe{}} A pixie in the Court of Flora and Fauna that you are a little worried about. \cFWanabe{\They} \cFWanabe{\does}n’t seem to have many friends, or be happy very often.
\end{contacts}

\end{document}
