\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cFHead{}}

You are \cFHead{} (\cFHead{\They}/\cFHead{\Them}). You are calm and competent, organized enough to give any structure pixie a run for their money. Your affinity is for Dahlias and other flowers with capitula (daisy-like) structures. You are in charge of the Flora and Fauna pixies this evening, and are excited about your first time as the senior pixie. Your mentor is the current head of the Court of Flora and Fauna. You were honored when they chose you to be in charge of the delegation tonight. You know it’s supposed to be super chill and all, but it’s still a big deal to be publicly tasked with this.

The only thing that your Court needs to do tonight is shepard home the lunar moths who are returning from the mortal world, laden with mortal magic, and send off the solar butterflies for their two years of collecting magic. \cFButterfly{} is an incredibly talented Fauna pixie with a special affinity for Lepidoptera (butterflies and moths). This made them the natural choice to be in charge of the change over. Unfortunately they have pretty intense social anxiety, and often come across as timid and shy - not great for organizing such a big migration. You hope to cheer them on tonight and show them that having anxiety doesn’t prevent them from doing big, important things.

You are so excited that your best friend of decades, \cSPM{}, is returning from the away team tonight. While you understand why \cSPM{\they} had to go and be in charge of the away team, you fervently hope that you can both stay in Neverland this cycle. In the time \cSPM{} was gone, you grew a lovely little chrysanthemum from a seed you had \cSPM{\them} carry around in \cSPM{\their} pocket for a few weeks before they left. You were hoping to present them with the plant tomorrow as a welcome back gift, but when you went to check on it one morning two weeks ago (like you do every morning), it was wilting! You’ve been doing everything you could, even sneaking 1 more unit pixie dust than you are technically allotted, to try to perk it back up (not a big deal, the Magic Pixies always keep a bunch of extra units on hand in case of an emergency). Nothing has worked. A little cloud of worry has hung over your head ever since. Hopefully it is just a very unfortunate coincidence.

The other pixie on your mind is \cFTitan{}. \cFTitan{\They} \cFTitan{\are} a particularly inquisitive pixie, with a proclivity for history and research. \cFTitan{\They} spend\cFTitan{\plural} a lot of time out and about, exploring Neverland. Particularly around the area where the remains of the 4 titans who saved Neverland rest. A \textbf{lot} of time. While \cFTitan{\their} expertise is in pika and other lagomorphs (the family including rabbits and hares), and it is quite rocky in that area, it’s still a \textbf{lot} of time. \cFTitan{\They} \cFTitan{\are}n’t the most reckless pixie you know; that would be their new best friend, \cEAirship{}. You are a touch concerned that \cFTitan{} might be cooking up some terribly dangerous plan.

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Help \cSHead{} decide on an away team. You aren’t sure who among the Flora and Fauna pixies is the best one to send, but you know that you do not want to go, unless for some reason \cSPM{} wants to go again (unheard of).
	\item Support \cFButterfly{} with the lunar moth and solar butterfly migration. Hopefully \cFButterfly{\they} won’t actually need your intervention, but \cFButterfly{\they} \cFButterfly{\have} some social anxiety, and could use a cheerleader.
	\item Catch up with \cSPM{}, who has been on the away team these past 2 years.
	\item Keep an eye on \cFTitan{} and make sure they aren’t up to anything dangerous.
\end{itemz}

\begin{itemz}[Notes]
	\item Flora and Fauna pixies tend to understand ``goodbye'' better than most other pixies, since animals and plants don’t live forever the way pixies do. They still aren't very good at it.
\end{itemz}

\begin{contacts}
	\contact{\cSPM{}} A very old, very dear friend. These past two years have been rather lonely without \cSPM{\them}. You can’t wait to curl up in your favorite corner with tea, and exchange stories. Hopefully the worry you feel is just old Flora and Fauna superstition and everything is fine.
	\contact{\cFButterfly{}} Kind of your protege, you are hoping that by putting \cFButterfly{\them} in charge of the migration, it will help grow \cFButterfly{\their} confidence despite the anxiety.
	\contact{\cFTitan{}}  A Flora and Fauna pixie that is showing an unhealthy amount of interest in the Titans that originally closed off Neverland from the Mortal World.
	\contact{\cFWanabe{}} A Flora and Fauna pixie you don’t know well; they always seem melancholy to you.
	\contact{\cFHeart{}} A Flora and Fauna pixie you don’t know well; they always seem jubilant to you.
\end{contacts}

\end{document}
