\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cFTitan{}}

You are \cFTitan{} (\cFTitan{\They}/\cFTitan{\Them}). You love adventure and exploring, especially with your new best friend \cEAirship{}. The rabbits, hares, and pikas of Neverland that you are especially gifted with are always happy to tip you off to fun new adventures. You aren’t reckless, exactly, but you may have leapt before you looked a few times. But that’s what wings are for, right? Still, this time you've been extra diligent in your research and preparations. You even recruited a like-minded collaborator, \cETitan{}, and your new friend \cEAirship{} is helping too! You are going to revive the four Titans that saved Neverland so long ago by limiting the contact between the worlds. It’s the least you could do for them, after they saved everyone right? 

This all started some decades ago when you were exploring a particularly rocky area of Neverland to the north of Pixie Hollow. The Pikas there love playing hide and seek with you. When you were flitting around, finding a good hiding spot, you encountered a huge boulder that emanated heat! How strange? After the game, the Pikas told you about 3 other weird boulders in the area. Eventually you figured out that these were the remnants of the four great elemental Titans from history.

You quickly realized that most of the Pixies of Pixie Hollow thought that messing with magic as big as the titans was too big for Pixies. Your questions became more subtle, your research more clandestine. You don’t like having to kind of skulk around, but sometimes you have to do what’s best, even if it isn’t popular. One day sneaking around the library, you crashed (literally) into your now co-conspirator, \cETitan{}. \cETitan{\They} \cETitan{\were} doing the same as you - looking for information on the Titans! It seems that \cETitan{\they} had come to the same conclusion as you, that reviving them was the right thing to do. So the two of you joined forces.

\cEAirship{} joined the picture much later. The two of you met at an afternoon tea mixer a few months back, and became fast friends. Some might call \cEAirship{} a bit of an enabler. You prefer to think of \cEAirship{\them} as a cheerleader. Some days you wonder a bit about the fact that your two closest friends and allies are both Elemental Pixies. Maybe silo-ing people into courts isn’t the best way to take advantage of everyone’s skills. You’d never have gotten this far without the cross court collaboration. You really hope that none of you get sent on the away mission (since you can’t all go together because only one pixie from each court is sent).

Obviously the preparations haven’t been easy. This is no simple task, and you’ve been researching, planning, and preparing for years. Still, for the final preparation step, you and \cETitan{} had to borrow some of the spare pixie dust that the Magic pixies keep on hand (4 units), and some of the extra seasons components that the Element pixies make as buffer (5 units) - you would never have taken these without permission, except that no one believes reviving the Titans is even possible. And the resources you took are definitely extras. You triple checked. You have already spent these (pre-game) on preparations, so only the very last step remains. A ritual for four Pixies that must be completed once in Neverland, during the time while the portal to the mortal realm is open (so, tonight!). You’ll have to recruit at least one additional pixie to your cause to make this work. If you, \cETitan{}, and/or \cEAirship{}, decide you do not want to also take on the responsibility of living with the titans for 1000 years, you may need to recruit even more pixies to your cause to find 4 willing pixies for this part.


\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Revive the Titans! (see greensheet). Don’t get in trouble for “borrowing” some of the extra pixie dust and seasons components to do it.
	\item Avoid any of you or your friends getting sent on the next Away Mission.
	\item As a Flora and Fauna pixie, you really ought to help with the Solar Butterfly / Lunar Moth migration. But it’s so boring and tedious… Maybe reviving the Titans will make it unnecessary?
	\item Help \cETitan{} and \cEAirship{} with anything else they might be looking to accomplish tonight.
\end{itemz}

\begin{itemz}[Notes]
	\item Flora and Fauna pixies tend to understand ``goodbye'' better than most other pixies, since animals and plants don’t live forever the way pixies do. They still aren't very good at it.
\end{itemz}

\begin{contacts}
	\contact{\cETitan{}} Your collaborator in the secret plan to revive the elemental titans. You respect \cETitan{\their} intellect and gumption.
	\contact{\cEAirship{}} Your new best friend of only a few months. You enjoy \cEAirship{\their} wild enthusiasm and willingness to dive into things.
\end{contacts}

\end{document}
