\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cMAirship{}}

You are \cMAirship{} (\cMAirship{\they}/\cMAirship{\them}).  You are a maker pixie: a gifted gadgeteer, a mechanical magician, an engineering Einstein, an illustrious inventor, and you are consumed by a catastrophic crush.

The pixie economy is in shambles, and you think you know the real cure.  There are no animals suited for carrying the fruits of pixie labor, so pixies are limited to what they can carry in simple wheelbarrows, or with their wings; the average pixie can generate between six and eight dewdrops of lift, which isn't a particularly large amount.  You have a plan to revolutionize transport however: with \cEAirship{}, a fire pixie, you have invented lighter-than-air transport, which will revolutionize pixiekind.  You can build an airship with hot air as the source of lift, only needing pixies to provide heat and horizontal movement, not spending any effort lifting the load.  

There's one caveat, though.  The two of you have tried everything you could think of to get around it, but the truth is that for long flights (more than about 20 minutes), or heavy loads (more than about 2000 dewdrops), you either need so many fire pixies to heat the air inside the balloon-like canopy that you might as well carry the stuff yourself, or you need something that will distribute the heat evenly and consistently. And this is where iron comes in. You tried with rocks, you tried with glass, you even tried with copper. But there is no getting around the fact that iron has weird interactions with pixie magic that you hope will allow a single fire pixie to lift and maneuver an entire airship full of supplies, maybe with the help of an air pixie or a fast flyer from the Court of Structure to help with steering.

The only place to get iron is the mortal world. You plan to try to sneak through the open portal and snag some tonight. Or you could end up on the away team, but ugh, having to wait two whole years before you can see if your plan works? No way; that’d take too long! And why sneak? Well you don’t think that the Structure Pixies will let you bring iron into Neverland, at least not until you prove how cool your concept is (and that it works; which it doesn’t without the .iron.)

While passing the time waiting for the portal to open, you went to a flower party a few months ago, and met \cETitan{}.  You were instantly infatuated; you \emph{hope} you weren't too obvious, but you certainly hung onto their every word.  \cETitan{} confided to you that \cETitan{\they} want\cETitan{\plural} to raise the Titans that were left as mere candle flickers of their former blazing glory after they saved Neverland. You think that it’s a very noble thing to do to revive them, and you’re happy to support \cETitan{} – and hope to get closer to \cETitan{\them} in the process.  Sure, the Titans gave up their existence to prevent iron from destroying Neverland, but \cETitan{} thinks it'll be fine, and you wouldn't dream of telling \cETitan{\them} \cETitan{\theyare} wrong about anything.

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Make the airship work by acquiring and installing a piece of iron. Then present the idea to the Court of Structure and win their approval to build more.
	\item Win \cETitan{}'s affections.
	\item Support \cETitan{} in reviving the Titans.
\end{itemz}

\begin{itemz}[Notes]
	\item Only Maker pixies can put out a request for extra basic supplies (OOC: represented as paper, pipe cleaners, glue, etc) to be brought to the Great Hall. Only Magic pixies can put in a request for extra pixie dust.
\end{itemz}

\begin{contacts}
	\contact{\cEAirship{}} The elemental pixie who is helping you build the first ever ``airship’’.
	\contact{\cETitan{}} Your crush.  They seem excited to revive the Titans, and you are happy to help, if it will allow you to spend more time with them.
\end{contacts}

\end{document}
