\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cMChange{}}

You are \cMChange{} (\cMChange{\They}/\cMChange{\Them}). You are the Magic and Maker pixie returning from the Away Team. In your pocket is a piece of \textbf{cold iron}, but the weight in your pocket doesn’t remotely approach the weight on your heart. It is your fault that \cFLost{} is dead. But you suppose it’s best to start at the beginning.

You are a Maker pixie to be precise, but it’s hard, and it’s boring. From almost the first day in your personal workshop, you have done very little making, and an awful lot of watching out the window as the Flora and Fauna Pixies flitted here and there, helping all of the animals and plants. They are so much friendlier, and more social, than your fellow Magic and Maker Pixies. You have always wished you could be one of them.

Eventually you found a like mind in \cFWanabe{}. \cFWanabe{\Theyare} a Flora and Fauna pixie, who is equally, or maybe even more unhappy with \cFWanabe{\their} lot than you are. You put your heads together over many long years, and eventually worked out a dangerous and reckless ritual that you think will allow you to switch your magics.

Two problems remained. One, \cFWanabe{} doesn’t want Magic and Maker magic. You can’t blame \cFWanabe{\them}; you don’t want it either. \cFWanabe{\They} want Structure magic. And the transfer will have to be consensual. Two, there’s no getting around the fact that something as unconventional as switching your magic around requires a truly unconventional ingredient: cold iron. \cSAdvisor{} turned out to be both solutions in one. You’d almost given up hope of ever finding a Structure pixie who wasn't wholeheartedly delighted to be so, and you’d never have guessed \cSAdvisor{} was unhappy, but by luck or fate, or something, you found out.

\cSAdvisor{} wants to be a Magic and Maker pixie! And, \cSAdvisor{\they} had the authority to get you onto the Away Team, since the Mortal World is the only source of cold iron. So off you went. You spent the entire assignment looking for an opportunity to slip off. But \cSPM{} has eyes like an eagle, and has got to be the most rules obsessed Structure pixie you’ve ever met (and that is saying something since the Structure pixies write the rules).

With only one week remaining on the mission, you got desperate. You left the safe haven where the Away Pixies live, and struck out into the real world. You found a garden shed surprisingly nearby with a broken window. You slipped inside and started searching the shelves. There! A mug full of rusty old nails and stuff. If those weren’t iron, you didn’t know what was. You got a leaf to try to protect your hands, and sent to start trying to tug one free.

A voice behind you cried “what are you doing?” You whirled around. You were followed! By \cFLost{}! \cFLost{\They} hovered there, hands on \cFLost{\their} hips. Then the mug full of nails teetered, and fell, in agonizing slow motion, with you under it! In that moment, you knew it was all over. And then you felt something - no - someone slam into you, pushing you out of harm's way.

No! No, no, no, no no! \cFLost{} was trapped under a pile of nails. \cFLost{\They} screamed. You couldn’t begin to imagine how much it must hurt! You rushed forward, grabbing at a nail to try to pull it free. It burned you. You darted outside to grab leaves and came back. But you couldn’t get a grip on the nail through the leaves. You tossed them aside and went back to trying to pull at the nails with your bare hands. You couldn’t think of anything but trying to get \cFLost{} out. \cFLost{\They} saved you. It should have been you. The next you were furious. If \cFLost{} hadn’t followed you, you wouldn’t have been startled, wouldn’t have caused the mug to fall. No one would have had to get hurt. You tried to shut your mind to the pain, but the blisters that formed on your hands were impossible to ignore. Try as you might, you could only get three of the dozens of nails free. You sobbed, you screamed, you struggled. 

Finally, you remembered that you weren’t alone. In the fading light of day, you rushed outside and threw a shower of sparks into the air - a Pixie distress call. You hoped beyond hope that \cSPM{} and \cELove{} would come, and could somehow fix this. You don’t remember much about what happened after they arrived. It all felt like a nightmare. Somehow \cELove{} got \cFLost{} out from under the pile.  At least the three of you were able to hold \cFLost{} as \cFLost{\their} light went out.

When the three of you left that accursed place, you watched your hands wrap a small chunk of iron in the leaves and mud that you didn’t remember having been put on your own hands to soothe the pain. Now it’s in your pocket. Safe enough for now, in its muddy little shell that prevents you from coming in contact with it. You have what you need to accomplish the thing you thought you always wanted. Was it worth the cost?

Your one small blessing has been that \cSPM{} hasn’t yelled at you, or demanded you explain what happened yet. You have no idea what you will tell \cSPM{\them} when \cSPM{\they} do. You suppose you could lie. Say that you followed \cFLost{}, and not the other way around. Would that be a disservice to \cFLost{\their} memory? You expect that \cSPM{} will demand an explanation soon. \cSPM{\Theyare} expected to provide \cSHead{} a report on the mission once the portal opens.


\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Decide what to tell \cSPM{} and \cELove{} and everybody else about what happened.
	\item Decide if the price paid is worth it to switch your magic to Flora and Fauna magic. Remember that \cFWanabe{} and \cSAdvisor{} are both counting on you too.
	\item Try to find some comfort, or solace, or atonement, or forgiveness, or something.
\end{itemz}

\begin{itemz}[Notes]
	\item Only Maker pixies can put out a request for certain basic supplies used in things like building Season Units. to be brought to the Great Hall. Only Magic pixies can put in a request for extra pixie dust.
	\item The \iMudCase{} you have with you contains the piece of Cold Iron. The mud ball is currently protecting you from taking any damage, but neither can you use the iron to do anything. Once the mud ball is broken open, it cannot be repaired; the iron will be exposed and anyone who comes in contact with it will suffer damage.
\end{itemz}

\begin{contacts}
	\contact{\cFLost{}} The Flora and Fauna pixie on the Away Team who is now dead because of you.
	\contact{\cSPM{}} The Structure pixie in charge of the away team. A real stickler for rules who for some reason hasn’t yet yelled at you for leaving the safe haven.
	\contact{\cFWanabe{}} A Flora and Fauna pixie who wants to trade \cFWanabe{\their} magic for Structure Magic.
	\contact{\cSAdvisor{}} A Structure pixie who wants to trade \cSAdvisor{\their} magic for Magic and Maker magic.
\end{contacts}

\end{document}
