\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cMHead{}}

You are \cMHead{} (\cMHead{\They}/\cMHead{\Them}) and a keen Magic pixie. You are open and gregarious, always happy to share your workbench with other inquisitive minds. You delight in the study of Pixie Dust and its myriad uses. Being head of the Court of Makers and Magic takes away some of the time you’d like to be experimenting, but someone has to do it, and you don’t actually mind the excuse to chat with Pixies from every court. There are so many fascinating and entertaining personalities in Pixie Hollow.

As head of the Court, your primary focus tonight is on arranging the next Away Team. You’ll need to pick someone from among your court to go on the next Away Team. Last time the choice was obvious. \cMChange{} was clearly in need of a change of scenery. This year you’re not so sure. \cMIron{} is eager - too eager, because \cMIron{\they} are convinced that the next big breakthrough for Pixie-kind will be in the study of Iron (!) You are pretty sure if there is anything that could kill a pixie, it’s iron. You’d like to send \cMAirship{}, but you don’t know if you will be able to convince them to leave behind whatever \cMAirship{\their} current project is. It’s been keeping \cMAirship{\them} up into the wee hours of the morning for months. 

And then there’s \cMTree{}. That kid really needs to learn how to slow down and take a breath. \cMTree{\They} \cMTree{\are} always running here and there, giving the fast flying pixies a run for their money. Everything is a crisis to \cMTree{}. Never have you had a pixie more inclined to cry wolf as it were. But you can’t imagine inflicting \cMTree{\their}\ldots enthusiasm on someone else unless they were well seasoned. In other words, it might depend on who is selected to lead the away team as to whether \cMTree{} would be an appropriate choice.

Running a Court is a lot to think about. Enough to keep any pixie busy. What with the teaching and mentoring, and serving as a safety board when some Pixie decides to try to build roller skates for squirrels or something. So it’s been a bit of a stretch to support your metamour \cFButterfly{} for these past two years. The two of you both have \cFLost{} as a partner, and \cFLost{} went on the away team with \cMChange{}. So you’ve been using what little free time you have to try to support \cFButterfly{}. The truth is that you don’t understand the how anypixie could be so painfully shy and nervous all the time. It’s not like the other pixies are going to bite.

Still, you like \cFButterfly{} well enough, and you share \cFButterfly{\their} excitement about \cFLost{}’s return. The two of you have planted yourselves in front of the plinth where the portal to the Mortal World will open. In the 20 or so minutes before it opens, the air becomes sort of translucent, and allows pixies in Neverland to see shadows of the pixies on the other side. One, two, three\ldots three? Why do you only see three shadows on the other side of the portal?  You turn toward \cFButterfly{} who is standing beside you. The look in \cFButterfly{\their} eyes tells you \cFButterfly{\they} \cFButterfly{\are} having the same terrible, impossible thought as you. \textit{(OOC: the two of you will start in front of where the portal will open. You haven’t yet had a chance to voice anything to \cFButterfly{}, as you were waiting to see if something would change and a fourth shadow would appear. It will still be 15 minutes in game before the portal actually opens and you can see for sure what is happening.)}

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Help \cSHead{} figure out who to send on the Away team.
	\item Take care of your court and prevent \cMTree{} from raising any unnecessary alarms, \cMAirship{} from attempting any dangerous feats of engineering, and keep \cMIron{} away from any possible chance of encountering iron somehow.
	\item Support \cFButterfly{} however you can. You’ve got a bad feeling about \cFLost{} and the returning away team.
\end{itemz}

\begin{itemz}[Notes]
	\item Only Maker pixies can put out a request for certain basic supplies used in things like building Season Units. to be brought to the Great Hall. Only Magic pixies can put in a request for extra pixie dust.
\end{itemz}

\begin{contacts}
	\contact{\cFButterfly{}} Your metamour. A terribly anxious Pixie. You’ve done your best to support \cFButterfly{\them} while \cFLost{} was on the Away Team, but you just don’t understand \cFButterfly{\their} social anxiety and that makes it hard.
	\contact{\cMTree{}} An excitable pixie who always treats every little bit of progress like the \textbf{best thing ever} and every tiny setback as the \textbf{worst thing ever}. You spend a lot of time somewhat ineffectually trying to get \cMTree{\them} to see a little perspective.
	\contact{\cMChange{}} A restless pixie you assigned to the Away team two years ago, in the hopes that it would help settle \cMChange{\them}. You look forward to seeing how \cMChange{\they} \cMChange{\have} grown and changed.
	\contact{\cMAirship{}} A clever pixie with big dreams. Possibly too big? \cMAirship{\They} tend to start building before \cMAirship{\they} \cMAirship{\have} finished their safety review.
	\contact{\cMIron{}} A particularly stubborn and problematic pixie. You try not to think of anyone as a thorn in your side, but you’ve run out of ideas for what to do with a pixie that talks about studying iron (!). You need to keep an eye on anyone spending time with \cMIron{} lest they enable \cMIron{}’s worrisome behavior.
\end{contacts}

\end{document}
