\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cMIron{}}

You are \cMIron{} (\cMIron{\they}/\cMIron{\them}).  You have always been inspired to solve problems, to innovate solutions, but you have what could be the most unusual interest in the history of pixiedom: you are an iron nerd.  More than that: you think you've cracked one of the most important problems to pixiekind, making iron safe to be around.

You haven't been able to test it out on any real iron – it obviously couldn't be brought to Neverland until it was already made safe.  You wouldn't even have a chance to prove your theories if you caused any accidents.  That said, your magic has been successful on all the tests you could do in Neverland, and you feel confident you know what you're doing.  You know there will certainly be an opportunity soon to visit the human realms, where you can do all the experimentation you need – if you could go there and prove your technique works, you would be a legend among pixies forever.  Pixie children would write pixie essays about you in pixie elementary school, titled "The Amazing \cMIron{}: Saving Us From Iron," and would get at least a B+.

Unfortunately, the resources you need – 20 units of pixie dust – wouldn’t be available to support your research on the other side. Pixies have a certain amount of inherent magic - what allows them to fly, what allows them to access their special talents, but one of the hardest things about being on the away team is the lack of pixie dust. Pixie Dust only keeps for about 2 weeks, so for the vast majority of the Away Mission, the pixies do without dust, which is used for particularly strong or unusual effects - like neutralizing iron.

Tonight, the portal will be open. You could duck through and flit off into the mortal world and find a piece of iron. But it does you no good unless you can convince \cMHead{} or \cMTree{} to give you every scrap of spare pixie dust -- all 20 spare units that the Magic Pixies keep on hand for emergencies. You doubt that’ll work.

So, it would be an awful lot more convenient for you if the portal would just stay open permanently, instead of closing. You’ve found three like-minded friends who are going to help you make this a reality: \cSLibrarian{}, \cFHeart{}, and \cESweet{}. Together you have a \textbf{secret} plan to prevent the portal from closing so everyone can watch the seasons spread through the mortal world. You’ve squirreled away quite a stockpile of pixie dust and infused the components needed for the ritual that the librarian/archivist designed. The ritual happens in 2 parts. The four of you must complete most of it here, and then exactly 1 of you must be part of the away team to perform the final step on the mortal side of the barrier. Then the portal will be blown back open, never again to close. Then you could save up pixie dust from your daily allotment, or “borrow” a little extra at your leisure to prove your theory.

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Work with \cSLibrarian{}, \cFHeart{} and \cESweet{} to permanently open the portal to the mortal world.
	\begin{itemize}
		\item Perform the Neverland side of the ritual before the Away Team is sent off.
		\item Get exactly 1 of you (preferably \textbf{not} you) on the Away Team, to complete the last step (in the last 15 minute of game).
		\item If the plan to permanently open the portal fails, you at least can go see it for yourself.
	\end{itemize}
	\item If the opportunity presents itself, demonstrate your theories about how to make iron safe to interact with right now.
	\item Maintain your public reputation: without trust and resources, you won't be listened to.
	\item
\end{itemz}

\begin{itemz}[Notes]
	\item Only Maker pixies can put out a request for extra basic supplies (OOC: represented as paper, pipe cleaners, glue, etc) to be brought to the Great Hall. Only Magic pixies can put in a request for extra pixie dust.
\end{itemz}

\begin{contacts}
	\contact{\cSLibrarian{}} One of your co-conspirators, who designed the ritual you will be executing on tonight.
	\contact{\cFHeart{}} One of your co-conspirators; you’re pretty sure this one is the Flora and Fauna pixie, but \cFHeart{\they} \cFHeart{\are} kind of hard for you to tell apart from \cESweet{}.
	\contact{\cESweet{}} One of your co-conspirators; is this one the Flora and Fauna pixie? No, this one is the Element pixie - you think. \cESweet{\They} \cESweet{\are} kind of hard for you to tell apart from \cFHeart{}.
\end{contacts}

\end{document}
