\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cMTree{}}

You are \cMTree{} (\cMTree{\They}/\cMTree{\Them}). You are a worrier. You tend toward seeing the worst possible outcome of any risky situation, and maybe\ldots sometimes\ldots overreact\ldots a little. You are the most gifted Magic pixie, outside of maybe \cMHead{} \cMHead{\themself}, and you spend your time studying and taking care of the Tree of Time. Part of your day to day duties is to help hand out pixie dust allotments to every pixie, and carefully storing any spare pixie dust the tree produces.

Since Pixie Dust only keeps for about two weeks, it is important to maintain strict records and practice a “first in, first out” inventory system. You spend so much time with the Pixie Dust distribution and storage systems that you dream of dust - but that’s okay because they are your favorite dreams. Naturally you were the first one to notice that something was wrong. About a month and a half ago, something started to feel off as you watched the dust waft down into your collection bins. You went to your best friend \cSHelp{}, and told them your suspicion - that the Tree of Time was producing less Pixie Dust than it should.

At first \cSHelp{} thought you were over reacting (as usual). Maybe you shouldn’t have tried talking to at 2 am about this? But you eventually convinced \cSHelp{\them} to come help you count packets of dust. It took over a month of painstaking counting and careful record keeping to decimal places that Pixies never bother with, but even through the noise of the natural variation in how much dust the tree produces each day, a pattern emerged. The Tree of Time is producing approximately 7 units of pixie dust less today than it did three months ago. Three months ago, production was normal. Then \textit{something} happened.

This is bad. Very bad. Alarm raising at the highest echelons of Pixie Hollow bad. But \cSHelp{} has repeatedly cautioned you that without evidence as to the cause of the decrease, no one will believe the two of you. But where to start looking? Especially when you’re confined to the great hall of Pixie Hollow for the portal opening?  Your investigation has managed to narrow the suspects to the other pixies in here with you, at least. \textit{(OOC Note: You have a green notebook to share with \cSHelp{} to forward your investigation.)}

All of this wouldn’t be so bad, if it weren’t for every Pixie’s tendency to smuggle a little extra pixie dust for their pet projects. Oh yes, you know all about that. You know that on 5 different occasions in recent memory, between 1 and 5 units of pixie dust have disappeared from your store of spare. Which means that the Court of Magic and Makers is critically low on dust. You just hope that none is needed to deal with any kind of emergency tonight, because there are only \textbf{4} units left! You and \cMHead{} will have to be \textbf{very judicious} with anything you authorize their use for.

\begin{itemz}[Goals (in roughly descending order of importance)]
		\item Figure out why the Tree of Time started producing less Pixie Dust than it used to. You are somewhat reluctant to raise the alarm until you know who did it and how, if maybe not why. (See your Research Notebook)
	\item Fix the Tree of Time!!!!!
	\item Decide if any proposals to use pixie dust tonight warrant you calling in the last few units you have in storage.
	\item Keep an ear out for what pixies might have been doing with the extra dust they’ve been “borrowing”.
\end{itemz}

\begin{itemz}[Notes]
	\item Only Maker pixies can put out a request for certain basic supplies used in things like building Season Units. to be brought to the Great Hall. Only Magic pixies can put in a request for extra pixie dust.
\end{itemz}

\begin{contacts}
	\contact{\cSHelp{}} Your best friend. \cSHelp{\They} \cSHelp{\have} been helping you collect evidence that the tree is producing less dust. Now the two of you just need to figure out why.
	\contact{\cMHead{}} The head of the Court of Magic and Makers, and the only other magic pixie here tonight (therefore the only other pixie with the authority to call in pixie dust from the reserve.)
\end{contacts}

\end{document}
