\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cSAdvisor{}}

You are \cSAdvisor{} (\cSAdvisor{\They}/\cSAdvisor{\Them}). You are quick witted, clever, and protective of your best friend \cSHead{}. You don't quite have \cSHead{\their} patience, but no one makes things happen like you do. You are well liked, and well respected in Pixie Hollow. You are a favorite for the next \cSAdvisor{\Monarch}, but the truth is you don't want it.

Honestly, as nice as being part of the Court of Structure is, you really wish you had more interesting powers than rallying people to a cause and inspiring immediate action. What you really want to do is build things. The Court of Makers and Magic are the ones who build real things, the ones who create tangible evidence of their contribution. But such thoughts are taboo in Pixie Hollow. Everyone loves their magic - and besides, there's no way to change what type of magic you have. Or so you thought. 

Two and a half years ago, \cMChange{} approached you, saying that \cMChange{\they} and \cFWanabe{} were unhappy with their magic for their own reasons, and through a long investigation, and much secret trial and error had concocted a ritual that would could switch the magic one Pixie had with that of another. They were facing 2 problems: 1, the switch had to be consensual, and while \cMChange{} was happy with the idea of Flora and Fauna magic, \cFWanabe{} didn't want Maker and Magic magic, \cFWanabe{\they} wanted Structure magic, and 2, the ritual required a piece of cold iron, of which the only source is the real world. 

It was like a dream come true for you! You could have the kind of magic you wanted! Not immediately of course, but soon (at least as Pixies count time). You threw all of your considerable Structural weight behind making sure \cMChange{} was picked for the Away Team two years ago. Tonight, \cMChange{\they} will return with the final piece you all need. You'll have to find an excuse to slip away to an unwatched corner and perform the ritual tonight. There is no good or safe explanation for why any of you would be in possession of cold iron, which at best wreaks havoc with Pixie Magic. You do not want to get caught. But once the switch is made, no one can force you to unswitch! You just hope that \cSHead{} won't feel too betrayed by you following your heart.

Speaking of \cSHead{}, \cSHead{\they} \cSHead{\were} quite relaxed a moment ago, but then \cEHead{} whispered something in \cSHead{\their} ear. The worried look on \cSHead{}'s face tells you that something is up, and you'd better go find out what asap.

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Work with \cMChange{} and \cFWanabe{} to switch your magic to Magic and Makers. Don't get caught before the ritual is complete, otherwise you might be stopped.
	\item Support \cSHead{} with whatever \cSHead{\they} need\cSHead{\verbs}.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cSHead{}} Your best friend for approximately forever has always been \cSHead{}. You serve as \cSHead{\Their} \cSAdvisor{\heir}, which makes you essentially \cSHead{\their} second in command, Vice President, Royal Advisor, whatever you want to call it. Your day to day job is to address problems that Pixies bring, fielding questions and tasks that don't need \cSHead{}'s personal attention, so \cSHead{\they} have time for the things that really do.
	\contact{\cMChange{}}  One of the Pixies who created a ritual to switch around Pixie Magic. \cMChange{\They} \cMChange{\have} been on the Away Team these past 2 years, and should be returning tonight with a piece of \textbf{iron}, which is crucial for the ritual.
	\contact{\cFWanabe{}} The other Pixie who created the ritual to switch around Pixie Magic. \cFWanabe{\They} clearly feel\cFWanabe{\verbs} overlooked and under appreciated. You can sympathize, and hope that being part of the Court of Structure will suit \cFWanabe{} better than it ever suited you.
\end{contacts}

\end{document}
