\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cSHelp{}}

You are \cSHelp{} (\cSHelp{\They}/\cSHelp{\Them}). You are a quick learner, and curious about many things, but feel a little adrift. You are part of the Court of Structure, and have fast flying magic, but that isn’t enough to reveal your calling. You haven’t found your perfect calling yet, and you can feel the eyes of \cSHead{} on you, waiting for you to do something great. You respect \cSHead{\them} a lot, and don’t want to disappoint.

\cSHead{} does seem to sympathize with your uncertainty, and has given you carte blanche to help anywhere and with anything that strikes your fancy. It does mean you get to dabble in many things, and shadow any Structure pixie you want. Recently you’ve been working with the project managers helping the Elemental pixies prepare the Seasons. From everything you saw and heard and counted (oh geez, SO much counting) and sorted (SO much sorting).

You also hang out with the librarian, \cSLibrarian{} a lot. \cSLibrarian{} knows a lot about a lot of things, except for the Mortal World. Which has kind of piqued your interest in it. Maybe you could go on the away team? Except that whichever Structure pixie goes on the Away Team leads the team. Are you really prepared for that much responsibility? Maybe you should try to talk to \cSPM{}, who led the team that is about to return, and get their perspective?

And if you were to go with the away team, you’d at minimum have to find someone to take over your investigation. You probably should have started by mentioning that, huh? Anyway, after counting and counting and counting components for the Seasons, you were counting in your sleep. You never wanted to count anything ever again, until your best friend \cMTree{} showed up at your door in the middle of the night, two months ago, saying that \cMTree{\they} thought the Tree of Time was producing less Pixie Dust than it used to. 

If that were true, it would be a \textbf{huge deal}, and if it isn’t true, the two of you would be in \textbf{so much trouble} for scaring people. So the two of you got to counting little packets of pixie dust. You were \textbf{quite} skeptical at first, but once you collected enough data to see through the noise of the natural variation in production, the pattern became clear. The amount of dust has been dropping slowly over the last few months. Almost imperceptibly at first, but now it’s enough to really have you worried.

The two of you kept trying to convince each other that this was just a natural fluctuation, but the amount isn’t going back up again. It may be time to get help from more pixies… but on the other hand, will they believe you when the dust processing equipment is outside the area bounded by the wards for the portal opening? They won’t be able to verify your findings for themselves. You and \cMTree{} might need to find a root cause before you can get anyone to take you seriously.
 

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Find your calling and make \cSHead{} proud. \textit{(OOC Note: there is no one ``right'' answer to this. Go explore and find something that interests you!)}
	\item Decide if you want to be on the Away Team, and if so, if you will try to take on the responsibility of leader.
	\item Work with \cMTree{} to figure out why the Tree of Time is producing less Pixie Dust than it used to. \cMTree{} has a research notebook the two of you can collaborate on freely. You are very reluctant to raise the alarm until you know who did it and how, if maybe not why.
\end{itemz}

\begin{contacts}
	\contact{\cSHead{}} The \cSHead{\Majesty} of Pixie Hollow. \cSHead{\They} seem\cSHead{\plural} to have taken an interest in your future. You’re pretty sure this is a good thing?
	\contact{\cMTree{}} Your best friend, who approached you about the Tree of Time producing less pixie dust. The two of you counted output for months, hoping against hope that this was a natural fluctuation that would correct itself. Now you need to find the cause and get help reversing it.
\end{contacts}

\end{document}
