\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cSHead{}}

You are \cSHead{} (\cSHead{\They}/\cSHead{\Them}). You are kind and patient, and try your best (which is honestly quite good) to be supportive of your fellow Pixies. You act as a guide, a counselor, and a life coach as much as you act as a Governor of Pixie Hollow. Each leader leaves a mark on the community, yours is shaping up to be slow, but steady and sustainable growth and improvement. You are justly proud of this legacy. 

You are unsurprisingly Pixie Royalty, and part of the Court of Structure. This means that your magic centers around inspiring and encouraging people. You wish you had magic to help when decisions too tough for any other Pixie get dropped in your lap. Your title is technically \cSHead{\Majesty}, but you were duly elected in a fair and democratic election for a single 5 year term. The Pixies just never bothered changing the name of their leader to something less evocative of hereditary power. Don't squint too hard at the fact that only Structure Pixies are eligible to run for the role, and that a Pixie with Royal magic almost always wins.

You are tasked with overseeing everything, all the time. Thank goodness you have help. You delegate as much as you can to your cabinet and the rest of the Structure Pixies, all of whom are highly competent. You enjoy watching them excel in the roles you place them in. In your opinion, the most useful thing you do is assign the right Pixie to the right task.

Tonight in particular, your job is normally just to keep everyone safe and ensure that the best next Away Team is selected. The former is easy - there's no chance of serious danger in Pixie Hollow tonight. Most of the Pixies, as well as the other 8 types of magical creatures are carefully protecting your home - it wouldn't do for anything to interrupt the Pixies sending the Seasons through to the Real world. The guards have erected a series of nested magical barriers that protect the Great Hall of Pixie Hollow, and the dais upon which the portal will open. These barriers do prevent folks from entering or exiting the space, but messages and supplies can be sent through the barriers, should the need arise.

The latter is harder, since being on the Away Team is not something most Pixies are enthusiastic about. You'll need to collaborate with the Heads of each of the other courts to pick the right Pixie from each of the 4 courts. Each court has held back from guard duty the 3 or 4 candidates they've selected for your consideration. Technically someone returning from the previous away team is not precluded from being on the new one, but out of respect for their sacrifice, no pixie has ever been sent out twice in a row.

Unfortunately, this is not a normal portal opening. The Court of Elements has been reporting for months that they were on track, or even slightly ahead of schedule in producing the required supplies for the seasons. Just as the barriers for the evening were sealed up however, \cEHead{} hurried to your side and whispered in your ear that they are short several units for all of the seasons! \cEHead{\They} claim\cEHead{\plural} the missing units were stolen. You are not sure if you prefer the possibility of a thief in your midst, or that Elements has been overestimated their progress and lied to you to try to save face. Either way, you have a crisis on your hands. You are going to need help, and intend to task \cSAdvisor{}, your best friend and second in command with getting to the bottom of what really happened. You of course tasked \cEHead{} with determining if there is any way the units could be built (re)built before the portal closes.

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Task \cSAdvisor{} with doing whatever is necessary to find or replace the missing Seasons Units. (\cEHead{} has literally just told you this 30 seconds before the game start. You have not had time to take any action yet)
	\item Select a new away team.
	\item Keep everyone safe from any threats from the Mortal World or Neverland. \textit{(OOC Note: This goal is probably impossible to ``win,'' but working towards it will give you and other players truly game-shaping interactions)}.
	\item Receive the debrief report from \cSPM{}
\end{itemz}

\begin{itemz}[Notes]
	\item You must select the away team and send them through the portal at least 5 minutes before the end of the game. The portal will close with T-5 minutes to game end, so the Away Team must be in position by that time.
	\item You \textbf{can} order a pixie to be on the away team, or perform another task. You generally prefer not to use this authority, as over the long term it breeds malcontent; you'd much rather convince the pixie that it is in their best interest to do what you are asking.
\end{itemz}

\begin{contacts}
	\contact{\cSAdvisor{}} Your best friend for approximately forever is \cSAdvisor{}. Now \cSAdvisor{\They} serve\cSAdvisor{\plural} as your \cSAdvisor{\Heir}, which makes \cSAdvisor{\them} essentially your second in command, your Vice President, your Royal Advisor, whatever you want to call \cSAdvisor{\them}. \cSAdvisor{}'s day to day job is to address problems that Pixies bring, fielding questions and tasks that don't need your personal attention, so you have time for the things that really do.
	\contact{\cSHelp{}} You are quite fond of \cSHelp{} and see \cSHelp{\them} as something of your protege. \cSHelp{} is an incredible organizer, can spot inefficiencies a mile away, and have a list of half a dozen possible solutions before the birds have finished their morning chorus. For now, \cSHelp{\Theyare} tasked with helping anyone and everyone with anything they might need. You are sure that eventually \cSHelp{} will find a more narrow calling, and be able to really shine.
\end{contacts}

\end{document}
