\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cSLibrarian{}}

You are \cSLibrarian{} (\cSLibrarian{\They}/\cSLibrarian{\Them}). You are Pixie Hollow’s librarian and archivist, and obviously a member of the Court of Structure. You delight in your responsibility to collect and preserve as much knowledge as possible. Your only gripe is that there is an entire second world you don’t have access to. All you can do at the moment is sift through the information each away team happens to bring back, in the hopes of finding valuable nuggets of information.

Your library has a lot of information about a lot of things. What it doesn’t have is a lot of information about the human world. It’s *hard* to collect information about the human world. You were on the away team once, about half a millenium ago, and even with two years to flit around and explore, you know you barely scratched the surface. No, what you really need is a permanent path to the Mortal World that you and dozens of other Structure pixies can pass through freely to study it.

You’re not stupid. You know that the mortal world is dangerous, what with all the Iron and stuff, but you’re not stupid. You can avoid iron and still study the world. You’ve read the historical accounts dozens of times and you are sure the titans acted hastily to close Neverland off from the mortal world. It’s quite lucky they didn’t quite succeed and a small portal opens occasionally, otherwise they’d have ended Neverland faster than iron ever could.

So you’ve found yourself a \textbf{secret} group of like-minded pixies and have a plan to force the portal to stay open permanently. \cFHeart{}, \cESweet{}, and \cMIron{} all have their reasons to want the portal to stay open. Naturally you have to wait for the portal to open before you can prevent it from closing, so the four of you have been preparing for tonight for some time. \cMIron{} has squirreled away quite a stockpile of pixie dust to power the ritual that you designed. The ritual happens in two parts. The four of you must complete most of it here, and then exactly one of you must be part of the away team to perform the final step on the mortal side of the barrier. Then the portal will be blown back open, never again to close. So you’ll need to do what you can to get one (and only one) of the others on the Away Team.

Last night you were so excited about today that you couldn’t sleep. You gave up trying and took a little flight around the area. Down on the beach, an area frequented by M\&M pixies looking for things that wash up on the shore from the mortal world, you found a little glass bottle (clear glass, dark blue liquid inside). Now a bottle that’s little for a Pixie is quite noteworthy to have come from the mortal world. So you picked it up and examined it curiously. There’s some liquid inside it. You uncorked it, and took a sniff. It reeks! You stoppered it back up, and brought it back to study. There’s no sign of anything in your meager records of the mortal world of what this could be. The more you stare at it, the more you wonder if it wasn’t made in Neverland. But if so, to what purpose? It’s a cute little mystery to occupy your mind until it’s time for the ritual to keep the portal from closing.


\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Execute the ritual to keep the portal to the mortal world open forever.
	\begin{itemize}
		\item Perform the Neverland side of the ritual before the Away Team is sent off.
		\item Get exactly one of you (preferably you personally) on the Away Team, to complete the last step (in the last 15 minutes of game).
		\item If the plan to permanently open the portal fails, you at least can go see it for yourself.
	\end{itemize}
	\item Learn everything you can about the mortal world from the returning Away Team Pixies.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cFHeart{}} A fellow conspirator in trying to keep the portal from closing. A bleeding heart if you ever saw one. \cFHeart{\They} worr\cFHeart{\verby} about the animals and plants of the mortal world without Flora and Fauna pixies to look after them.
	\contact{\cESweet{}} A fellow conspirator in trying to keep the portal from closing. Sweet enough to make your teeth hurt. \cESweet{\They} want\cESweet{\verbs} everyone to be able to observe the impact of their work, so that real improvements and adjustments might be made.
	\contact{\cMIron{}} A fellow conspirator in trying to keep the portal from closing. The most practical of the three, who has done a lot of preparation for this ritual. You don’t actually know why \cMIron{\they} want the portal to stay open, but there is no question as to \cMIron{\their} commitment to the cause.
\end{contacts}

\end{document}
