\documentclass[char]{PP}
\parindent=0pt
\begin{document}
\name{\cSPM{}}

You are \cSPM{} (\cSPM{\They}/\cSPM{\Them}). You are precise, organized, and no-nonsense; some might even call you gruff. You aren't hostile or aggressive, but gentleness, kindness, and patience with incompetence comes hard for you. You are well respected both in Pixie Hollow and on the Away Team, but honestly, you are getting too old for this shit.

Everything was going flawlessly with the away team until a week ago. Despite the strict prohibition on exploring the mortal world that you had instituted, you woke up one morning to find \cFLost{} and \cMChange{} gone. You waited all day at headquarters, pacing anxiously and hoping those two would return on their own (technically the prohibition extends to search parties too; only a distress signal would allow you to leave your post).

In the fading light of dusk, you saw it - a shower of sparks thrown into the air. Such a signal was only to be used in the most dire of circumstances, as it might be noticed by the denizens of the mortal world. You and \cELove{} (the 4th member of the away team) hastened to the source - a garden shed. \cFLost{} was pinned beneath a cascade of rusty old nuts, bolts, nails and screws that had fallen from a spilled container from a higher shelf. \cFLost{\Their} light was dim and flickering. You'd never seen a pixie so weak or so hurt. \cMChange{} was crying hysterically, while trying to pull the bits and bobs off of \cFLost{}. Every time \cMChange{} touched one of the metal bits, it burnt \cMChange{\their} skin again. Clearly \cMChange{\they} had been trying for hours to free \cFLost{}, to no avail, before \cMChange{\they} finally called for help.

There was precious little you could do. Spreadsheets and time tables weren't going to fix this - weren't going to save a Pixie from Cold Iron. Only \cELove{} kept \cELove{\their} wits about \cELove{\them} as you stared in horror. \cELove{\They} pulled \cMChange{} away, wrapped \cMChange{\their} blistered hands in a leaves and soothing, cooling mud, and fetched sticks to build little levers that were safe to touch. You followed \cELove{}'s directions mindlessly. The immensity of the tragedy unfolding before you drove all thoughts from your mind. At least the three of you were able to hold \cFLost{} as \cFLost{\their} light went out.

You were about to round on \cMChange{} to demand what happened, but the absolutely shattered look \cMChange{\they} wore froze the reprimand in your throat. You know you've got to find out what happened, but for the whole week, you've been at war with yourself. \cMChange{} isn't even recognizable as the same Pixie \cMChange{\they} \cMChange{\were}. And \cMChange{\they} are really quite young as Pixies go. You have to know, but every time you try to bring it up, either you choke on the words, or \cMChange{} goes nearly catatonic and \cMChange{\their} eyes glaze over as tears pour silently down \cMChange{\their} face. You haven't had the heart, or the will, to force the issue. \textit{(OOC Note: this is partially a contrivance to allow PCs to play out this interaction and establish character dynamics.)}

Pixies don't know loss. \textbf{You've} never known loss. And here are \cELove{} and \cMChange{} looking to you for guidance. What are you supposed to tell them? How are you supposed to comfort them? You just want to be back in Pixie Hollow, tucked up in a corner with a mug of hot tea in your favorite acorn mug, and your old friend \cFHead{}. If anyone can help you understand loss, it's \cFHead{}. Plants and animals die at some rate right? Surely the F\&F pixies know how to say goodbye?

\begin{itemz}[Goals (in roughly descending order of importance)]
	\item Debrief the away team before returning to Neverland (you will have 15 minutes at the beginning of the game before the portal opens up in which to do this). Use this information to compose your report to \cSHead{}.
	\item Bear the bad news of \cFLost{}'s fate to \cFButterfly{} and \cMHead{}, who were \cFLost{}'s romantic partners.
	\item Keep an eye on \cMChange{}. \cMChange{\They} haven't been the same since what happened to \cFLost{}.
	\item Drink tea, have a little quiet time, and catch up with your friend \cFHead{}. You've damn well earned it.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cFHead{}} A very old, very good friend of yours. The two of you will surely have a lot to talk about over tea this evening. Maybe \cFHead{} can help you come to terms with the loss of \cFLost{}? You aren't sure it is fair to put this burden on \cFHead{}, but you don't know who else to turn to.
	\contact{\cELove{}} A member of the away team. A stalwart and reliable worker, and the only one who kept their wits about them as the tragedy of \cFLost{}'s fate was unfolding before you all. If you remember right, \cELove{} had a big fight with \cEHead{} just before the portal closed. Awkward given they were previously in a close relationship.
	\contact{\cMChange{}} A member of the away team. Normally lighthearted and cheerful, \cMChange{\They} \cMChange{\have} unsurprisingly become dreadfully melancholy since the tragedy with \cFLost{}. You wish you knew how to help \cMChange{\them}.
\end{contacts}

\end{document}
