\documentclass[blue]{PP}
\parindent=0pt
\begin{document}
\name{\bNeverland{}}

\section*{Neverland}
Neverland is a magical place, separate but inextricably tied to the real world. In the beginning, they were one and the same. The bronze age introduced the first schisms between the worlds. Bronze interacted poorly with magic; the iron that came next was even worse. Ultimately, 4 elemental titans sacrificed most of their power to close off the two worlds, leaving only a small portal that opens large enough for anything to pass through, 9 times over every 2 years. 

No such closing could be complete - it is not possible to entirely sever two halves of a whole and have them survive. The magic of Neverland must flow into the real world, else the real world will cease to exist, dragging its other half into the void with it. Each of the 9 groups of magical creatures of Neverland are tasked with creating and delivering some piece of magic to the real world during their assigned portal opening. The Pixies are tasked with the creation and delivery of the four seasons. Obviously they must do so in 2 year batches.

\section*{Pixie Hollow}
There are many sources of magic in Neverland, but for the Pixies, the most important one is their Tree of Time, which produces pixie dust year-round, the way that trees in the real world produce pollen in the spring. Pixie Hollow, where all Pixies live, is built in and around this Tree. From the tips of the tallest branches, to nestled among the roots deep under the earth; from that first hollow that gives the town its name, to the myriad structures that have been built out from the trunk - Pixie Hollow is made for Pixies, by Pixies, and is perfect for Pixies. Every Pixie has their own little house, and each of the four courts have communal work areas set up just so to suit their needs.

Pixies range far and wide across Neverland, collecting supplies, hanging out with the other magical creatures, and lending their skills to any challenges that might arise.

\section*{The Courts}
The four Courts of the Neverland Pixies are: Structure, Elements, Flora \& Fauna, and Makers \& Magic. The four courts mostly work in harmony and collaborate regularly. When things get tense, either between individuals or Courts, Structure Pixies step in to mediate. If you expect intense intrigue, bitter competition, and brutal betrayal, you are mixing the Pixies up with the Fae.

\paragraph{The Court of Structure} houses all Pixies with powers that facilitate organization, peace, and harmony. Here you will find the Pixie Royalty, those skilled in flying exceptionally fast, and project managers. Nothing would get done in Pixie Hollow without their help and coordination. While the head of government is referred to as King/Queen/Majesty, they are elected in a fair and democratic election for a single 5 year term.

\paragraph{The Court of Elements} houses Pixies who can control the five elements (fire, water, earth, air, light). Every Pixie in this court has some basic ability with all five, but a clear aptitude for one. With the help of the Court of Structure these Pixies are tasked with building the actual components of the seasons, and combining them in the correct ratios. By the night of the portal opening, everything is prepared and the Court of Elements can kick back, relax, and enjoy their job well done.

\paragraph{The Court of Flora and Fauna} houses all Pixies skilled in communicating with and raising plants or animals. Pixies in this court will be skilled with plants, animals, or the things that are hard to classify. They usually specialize in one species or a few related ones, but can provide basic support for anything in their purview. This Court is in charge of ensuring that the Lunar Moths and Solar Butterflies switch places during the Pixie portal opening. These magical creatures collect and bring back the magic of the real world (hope, joy, laughter, etc) to Neverland, closing the cycle and sustaining Neverland in turn.

\paragraph{The Court of Makers and Magic} houses those Pixies who excel at building and repairing  things, and collecting, refining, and imbuing objects with pixie dust. You find the real dreamers of Pixie Hollow here. Whatever the next big thing is, you can bet it’ll come from the Court of Makers and Magic. If anything goes wrong, there’s no one better than a Maker Pixie to troubleshoot it. If something needs an extra kick of energy, you need a Magic Pixie.

\section*{The Portal}
Conveniently, when the Pixies are supposed to send the seasons, the portal connecting Neverland and the Human world opens on a dias in the Pixie’s Great Hall. For about 15 minutes, the portal slowly “expands,” although the visual experience is more like watching an area of space becoming translucent and then transparent. (\textbf{Note}: The portal will be in its translucent state for the first 15 minutes of game, allowing the Pixies in the Great Hall to see silhouettes of the Away Team, but not hear them or interact with them. At the 15 minute mark, the portal will open all the way and the Away Team will be able to step through and return to Neverland.)

\subsection*{Magical and Mundane Supplies}
During the time of the Portal opening, the Great Hall of Pixie Hollow is warded off by ancient and powerful magic. These wards prevent most things from going in, or out, during this sensitive time. Nothing as big as a Pixie can pass through \textit{(OOC Note: your characters are all stuck here until the portal closes and the ward dissipates)}. Messages can pass both ways, as can Solar Butterflies and Lunar moths. Additionally, supplies for building magical and mundane creations (like season units) can be brought in, and small creations can be sent out. Each court is able to call in different types of resources that may be needed for a project. \textit{(OOC Note: This is a kludge to force characters to talk to each other, collaborate, and strategize. Further instructions are available at the ``Resource Station'' signs.)}

\begin{itemize}
	\item Structure Pixies can call for up to 2 units of paper (origami, construction, tissue, or round white circles) every 10 minutes.
	\item F\&F Pixies can call for 1 stamp \& stamp pad, or 5 leaf stickers every 10 minutes.
	\item Maker Pixies can call for up to 3 units of pipe cleaners or 3 cotton balls every 10 minutes.
	\item Magic Pixies can call for any quantity of pixie dust at any time, as long as there is supply available in storage.
	\item By the magic of the Element pixies, pens, glue, and scissors are freely available.
\end{itemize}

\subsection*{The Seasons}
The Court of Elements spends the time between portal openings creating the 160 units (plus a few extra) of the Seasons that is necessary for the seasons to occur in the human world. Each season takes 20 units to complete, effecting the world for between 4 and 5 days. The units have just over a 2 year shelf life, making it worthless to expend the time and effort to make more than is necessary. Just before the wards close, the Element Pixies bring all of the units into the Great Hall. \textit{(OOC Note: The bulk of season units are an abstract concept. The stock cannot be taken from, and unless \cEHead{} explicitly prevents it, the units will be transferred to the human world without any effort by the PCs. Season units built in game are represented by phys reps, and can be lost, stolen, traded, etc.}

\subsection*{Lunar Moths and Solar Butterflies}
Pixie dust is the most familiar source of magical energy, but there are others. The Lunar Moths and Solar Butterflies are one such source. The Butterflies/Moths spend 2 years in the human world, collecting the magic of that realm (hope, joy, laughter, etc). When the portal opens, they are guided by the F\&F pixies to return to Neverland. They will spend the next 2 years fluttering around Neverland, slowly disseminating the magic they picked up, and reinvigorating the world. Their counterpart follows the same cycle, but offset by 2 years. When the butterflies are in the human world collecting magic, the moths are in Neverland spreading the magic they previously collected. \textbf{It is possible to use the energy from the Solar Butterflies as an unrefined substitute for pixie dust at a 2:1 ratio - any mechanic that calls for pixie dust can use Solar Butterfly energy instead, but only \cFButterfly{} and \cFHead{} can authorize the use of butterfly energy in this way.}

\section*{The Away Team}
The Pixies can’t just throw the seasons through the portal and hope for the best. Someone must go with them, to ensure they are released at the right time. The Court of Structure is in charge of working with the heads of the other three Courts to select an away team, composed of 1  member from each of the 4 courts, to cross over into the real world and stay there for 2 years to manage the meting out of the seasons. It is a tough job - few Pixies do well being away from home and their loved ones for so long, but it comes with much prestige, and no one can argue it is not crucial to the continued survival of all.

The new Away Team must be on the human world side of the portal when the game ends and the portal begins to close. A team leader must also be agreed upon. By default, this is the Structure pixie on the team, but it is not unprecedented for a pixie from a different court to lead.

\section*{The Life Cycle of Pixies}
Pixies are of course born (as fully formed adults) from the first laugh of a baby in the real world. That laughter is one of the only things that can pierce the divide between the worlds when the portal is closed (Peter of course is the other. That boy is impervious to rules.) Actually, all magical creatures in Neverland are born of a baby’s first laugh, some become Pixies, others become titans, or merfolk, or something else. A new-born Pixie will naturally gravitate to a common tool of their type of magic within the first few minutes (e.g. a Maker Pixie might pick up a Hammer, a Fauna Pixie might reach out to pet a squirrel). Their Court welcomes them with great joy. For the first year, a Pixie is apprenticed to someone from their Court who shows them around and helps them get settled, kind of like an older sibling. Age doesn’t really matter to Pixies after that. 

Some Pixies have romantic relationships. Most have at least a few close friends. The structure of relationships are left up to the Pixies involved. Sometimes Pixies break up, or fall out with friends. Drama is not unknown to Pixie Hollow, but Pixies don’t often hold on to grudges the way unicorns do, and things usually blow over pretty quickly (usually in a matter of a decade or two).

Pixies don’t really know loss, because pixies don’t die. Instead, at some point, a Pixie becomes tired - very tired. When that happens, usually in the range of 500 to 1000 years after they were born, the Pixie seeks out a particular Magic Pixie, who makes special glass jars, and commissions one. In a beautiful celebration of life, the whole community joins the tired Pixie in the main cavern of the winding catacombs under the Tree of Time for a huge party. At the end of the night, the Pixie opens the glass jar, and they flow into it, becoming a tiny golden spark of light.  A close friend, partner, or the current leader of Pixie Hollow closes the jar, and sets it in an alcove, with the Pixie’s name engraved above it. (\textbf{Note}: This process is out of scope for this game; a Pixie can express tiredness and \textit{desire} to rest, but the \textit{Jar Maker} is not a PC, and not accessible during the time span of game.)

At any time in the future, a Pixie can pick up the jar, hold it close, and converse with the Pixie resting inside. On some few occasions, a Pixie has requested to be let out from their jar years later by turning silver. In those unusual cases, the caretakers (a mix of Structure and Magic Pixies) simply let them out, and they return to their normal life in Pixie Hollow.

\section*{Iron}
Iron nearly destroyed Neverland. The humans will never know or understand how close they came to destroying themselves when they created it. Away teams are strictly cautioned to stay as far away from anything metal as possible. While “cold iron” is the worst, pixies have found out the hard way that there is iron in a distressingly large number of things in the Real World. It is even rumored that extended contact with iron could \textbf{kill} a pixie - an unheard of, and unspeakable tragedy! (OOC: For this game, “Cold Iron” is defined as iron that was worked cold in part of its lifecycle. Most alloys including steel \textbf{do not} qualify as “Cold Iron” but still have iron in them.)


\end{document}
