\documentclass[notebook]{PP} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nTree{}}

\begin{page}{first}
\textbf{You can share everything in this notebook freely with \cSHelp{}.} 
This notebook represents your ongoing investigation. You've already narrowed your suspect list down to the pixies here tonight (except the Away Team, obviously they cannot be responsible.) \textbf{To continue your investigation}, open the next page at game start.
\end{page}

\begin{page}{second}
Examine the current state of the Tree of Time by placing 1 hand on a wall of the Great Hall, and following the wall all the way around the room, traveling slowly, until you return to your starting point. You will have circumnavigated the entire room (treat open doors as closed so you can continue without leaving the room). One character must either do this 2x, or have each of \cSHelp{} and \cMTree{} do it once. This represents carefully examining the state of as much of the tree as you can reach. After completing this, open the next page.
\end{page}

\begin{page}{third}
The Great Hall is one of the few places in all of Pixie Hollow that has access to the heartwood of the Tree of Time. This has given you new insights into the problem - specifically that whatever has happened to the tree, has happened among the roots. Unfortunately you cannot reach the roots right now, so you'll need to narrow your search another way. Fold and label a ``cootie catcher'' out of construction paper (you may need an Elements pixie to help by visiting \sResourceElements{}). This will represent your investigation narrowing down which court your target is in. Use the toy like a magic 8-ball and have at least 1 person from each court ask a question for you to answer using it. Once you've answered the questions, open the next page.
\end{page}

\begin{page}{fourth}
Your research indicates that the culprit who harmed the tree somehow is in the Court of Flora and Fauna. Interrogate pixies from that court until you find who did it, and how. Once you know, you can go public with your information and get the really important pixies, like \cMHead{}, \cSAdvisor{}, and \cSHead{}, to make the culprit fix it and promise never to do it again.
\end{page}

\endnotebook

\end{document}
