\documentclass[green]{PP}
\parindent=0pt
\begin{document}
\name{\gSesons{}}

All Court of Element Pixies know how to build Season Units. But we’re all done building units for this go around, right? Right? Any Pixie can help build units, and multiple pixies can collaborate. As long as at least one Element Pixie helps in a meaningful way, no pixie dust is required for the unit (see step 7)

\begin{enumerate}
	\item Prepare a vessel for holding season units by folding an Origami Masu Box using origami paper for EACH season. \textbf{You will end up with 4 boxes; 1 for spring, 1 for summer, etc} (Origami instructions available at the Court of Elements Table).
	\item All supplies must be called in by various courts. \textit{(OOC Note: This is a kludge to force characters to talk to each other, collaborate, and strategize.)}
	\begin{enumerate}
		\item The Structure Pixies can call for up to 2 units of paper (origami, construction, tissue, or round white circles) every 10 minutes.
		\item The F\&F Pixies can call for 1 stamp \& stamp pad, or 5 leaf stickers every 10 minutes.
		\item The Maker Pixies can call for up to 3 units of pipe cleaners or 3 cotton balls every 10 minutes.
		\item The Magic Pixies can call for any quantity of pixie dust at any time, as long as there is supply available in storage.
		\item By the magic of Element pixies, pens, glue, and scissors are freely available.
		\item \textbf{To request supplies: Visit the ``Resource Station'' signs for instructions}
	\end{enumerate}
	\item To make 1 unit of Spring: (1 rain scene = 1 unit)
	\begin{enumerate}
		\item Glue at least 4 cotton balls to the top portion of a half piece of construction paper to make one or more cloud shapes. You may pull them apart to suit your vision.
		\item Glue at least 3 raindrops made from bending pipe cleaners (color does not matter; 1 pipe cleaner per raindrop) to the remaining portion of the construction paper.
		\item Alternately, use at least 3 different colors of pipe cleaners to create a rainbow shape and attach it.
	\end{enumerate}
	\item To make 1 unit of Summer: (3 images or 1 scene = 1 unit)
	\begin{enumerate}
		\item Cut or tear small pieces of tissue paper.
		\item Glue to a half piece of construction paper to make a simple image or scene (e.g. A tree, a sun, an umbrella at the beach)
	\end{enumerate}
	\item To make 1 unit of Autumn: (1 collage = 1 unit)
	\begin{enumerate}
		\item Use stickers, leaf stamps and/or freehand drawing to create a collage of leaves on a half piece of construction paper. Collage must cover at least 80\% of the paper.
	\end{enumerate}
	\item To make 1 unit of Winter: (3 snowflakes = 1 unit)
	\begin{enumerate}
		\item Fold a round white construction paper circle up like pie slices.
		\item Use scissors to cut shapes out of the folded edges of the paper.
		\item Unfold to reveal the design.
	\end{enumerate}
	\item If the unit was made entirely by NON-Element pixies, 1 unit of pixie dust or solar butterfly energy must also be expended.
	\item \cEHead{} will receive the unit (aka: it is \cEHead{\their} job to keep count) and place the unit in the appropriate box. If \cEHead{} is unavailable, \cSHead{} can do this in \cEHead{\their} stead.
	\begin{enumerate}
		\item You may never have more than a 2 unit difference between the season with the most, and the season with the fewest units.
	\end{enumerate}
\end{enumerate}
\end{document}
