\documentclass[green]{PP}
\parindent=0pt
\begin{document}
\name{\gButterfly{}}

Everypixie in the Court of Flora and Fauna knows how the migration works, but \cFButterfly{} is \textbf{in charge}. Everyone should take their cues from \cFButterfly{\them} regarding what to do, and when. It’s not hard, it’s just a lot of work, and a fair bit of patience. The butterflies and moths must be attracted to the portal area by the creation and planting of some \textit{very special} flowers. The flowers' must be made within the confines of the wards, and planted as immediately as practical (see step 2). Once planted, they cannot be moved. The magical summoning effect of these flowers lasts for only 3 hours, so they cannot be prepared ahead of time.

\begin{enumerate}
	\item Construct 4 flowers out of pipe cleaners (use at least 2 colors for each flower) to attract the Solar Butterflies from the Mortal World, and the Lunar Moths from Neverland. These ethereal creatures can pass through the safety wards without issue. -- You can construct more flowers, and place them as game goes on, but you should prioritize making at least 4 as soon as possible.
	\item Place 2 flowers at “Sign 3” next to the portal and 2 flowers at “Sign 4” on the opposite side of the room. These will attract the butterflies and moths over time.
	\item Every 30 minutes, a number of butterflies/moths will be attracted, depending on how many flowers have been placed. \textbf{Each flower} can attract between 1 and 4 butterflies/moths. No more than 4 can cluster on 1 flower though, so if any have not been escorted (see below), fewer new ones may spawn. -- More flowers = more butterflies/moths you can attract at a time.
	\item Each butterfly must be “escorted” from “Sign 3” to “Sign 4”, and each moth from 4 to 3.
	\begin{enumerate}
		\item To “escort” a butterfly/moth, a Pixie must balance the phys rep (plastic gold or silver butterfly) on their open palm, and travel slowly from one sign to the other. If they travel too fast and the phys rep falls off, they must start over.
		\item \cFButterfly{} can escort up to 3 at a time.
		\item Other Flora and Fauna pixies can escort 2 at a time.
		\item Everyone else can escort 1 at a time.
	\end{enumerate}
	\item A minimum of \textbf{30 butterflies} must be escorted back into Neverland, and \textbf{30 moths} must be escorted out to the mortal world over the course of the event.
		\begin{enumerate}
		\item If you find you have fewer than 15 of each at the halfway point (1.5 hours into game), you are encouraged to construct additional flowers, to increase the spawn rate. - 30 is the expected average for 2 flowers over the duration for which the portal is open, but the number that spawn is random, and that can cause some swing and it is reasonable to want to hedge your bets.
	\end{enumerate}
\end{enumerate}

The energy carried by Solar Butterflies can be substituted for Pixie Dust at a 2:1 ratio (something requiring 1 unit of pixie dust would require 2 units of Solar Butterfly energy). If the energy is drawn from the butterflies this way, those butterflies will be deducted from the “escorted” count. Only \cFButterfly{} and \cFHead{} can authorize the use of butterfly energy in this way. The butterflies are not harmed in any way, they just no longer carry magic from the real world to spread across Neverland, because it has been consumed for some other use.

\end{document}
