\documentclass[green]{PP}
\parindent=0pt
\begin{document}
\name{\gPortal{}}

This ritual can be interrupted at any point. If interrupted, you must begin that \textbf{part} over. This seemingly straightforward and magic-less ritual works because you have already made extensive preparations and spent many magical resources in service to this.

\textbf{Part 1:}
These steps do not all need to be done one right after the other, but they must be accomplished in order, and before part 2 can occur.
\begin{enumerate}
	\item Identify the 4 pixies who will participate in this ritual; 1 from each court.
	\item Have each of the 4 pixies step through the portal to the mortal world, and back to Neverland.
	\item Gather around \cSHead{}’s throne (the chair on which they last sat). Walk around the throne 3x.
	\item Turn around and walk the other way around the throne 3x.
	\item Each Pixie participating must shake hands (or mime shaking hands) with the other pixies in the ritual, one at a time, while exchanging the phrase “I will the portal to stay open” (A total of 6 handshakes will be exchanged).
	\begin{enumerate}
		\item This is the riskiest part of the ritual, the most suspicious part, and therefore the part you are most likely to be caught at. It is NOT recommended that you do all of these handshakes all at once, or all in one spot. However, you must say the phrase loud enough that someone standing next to you could hear it. (you can’t just whisper in each other’s ears).
	\end{enumerate}
\end{enumerate}

\textbf{Part 2:}
\begin{enumerate}
	\item \textbf{Exactly 1} pixie who participated in the first part must be on the mortal side of the portal as it closes up (last 5 minutes of game).
	\item This character must place both hands on the surface of the division between worlds. It feels \textbf{weird} (feel free to roleplay accordingly).
	\item Recite “It is my will you shall not close” 3x.
\end{enumerate}

If both parts succeed, the portal will open back up immediately, never to close again. Over the course of centuries, this hole will grow bigger and bigger as the barrier between worlds slowly dissolves. (Unless somehow the Titans were to return and recast the spell to separate the worlds again.)

\end{document}
