\documentclass[green]{PP}
\parindent=0pt
\begin{document}
\name{\gSwitch{}}

This ritual can be interrupted at any point before step 7. If interrupted, participants must start over.

\begin{enumerate}
	\item Collect any pixies who wish to change their magic. These switches can be between as many pixies as you like, but must be consensual (no coercion).
	\item Agree on who each pixie is giving their magic to. No Pixie can end up without magic.
	\item Stand or sit in a circle and hold hands (or mime holding hands). 
	\item Place a piece of exposed \textbf{cold iron }in the middle of the circle / between the characters. The iron cannot be covered or concealed in any way. (The iron will NOT be consumed, and could be used again.)
	\item One character starts by saying “I give $<$Magic Type$>$, and receive $<$Different Magic Type$>$.” The character who is receiving the magic type from the first character repeats the statement from their perspective. Continue this among all of the Pixies involved until everyone has said this statement.
	\begin{enumerate}
		\item E.g. The first character says: “I give Structure Magic, and receive Flora and Fauna Magic.” The second character says “I give Flora and Fauna Magic, and receive Structure Magic.
	\end{enumerate}
	\item Repeat the process of going around with this statement as many times as you have participants. (if you have 2 participants, do the full circle twice. If you had 8 participants, you’d go around 8 times.)
	\item \textit{(OOC Note: From this point on, the ritual is NOT interruptible)} Everyone in the ritual reaches out to touch the cold iron at the same time, with their bare hands. It \textbf{hurts} your character a lot to touch it (feel free to roleplay accordingly, but check with nearby PCs before screaming since you will be in close proximity to them). Once your character makes contact, you cannot break it for 30 seconds. 
	\item After 30 seconds, your character lets go of the cold iron. The hand used to touch the iron cannot be used for tasks until it is healed by the expenditure of 5 units of pixie dust or solar butterfly energy, or 5 season units for \textbf{each} character healed. (This can easily happen post game; your character is not permanently harmed by this ritual.)
	\item See a GM for information on how your new type of magic works!
\end{enumerate}



\end{document}
